Analyzing Network Transfer Protocols on a Simulated Interplanetary Internet

### 2024-04-10 paper/paper.tex
Added citations

Messages between entities were assumed to be sent at the speed of light, as all
forms of radio, lasers, or other wireless messages all are sent at the speed of
light. Since propagation delay is much higher then terrestrial networks, other
delays (TODO specify which delays) were ignored as being negligible.

Based on these simplifications, a physical simulation with several goals. To
calculate if a line of sight could be made between two communicating entities,
that is if a message can be sent, to calculate the error rate when sending a
message, and to calculate the message propagation delay for the message to be
sent. Line of sight was achieved using simple geometry calculations. (See
appendix) All entities are able to block signals if the ray passes through the
radius of the entity. One of the largest factors contributing to transmission
error is the distance travelled by the electromagnetic signal between
transmitting and receiving nodes. By generalizing Friis' transmission formula
for isotropic emitters and receivers, we can obtain the ratio of signal
intensity received to signal intensity transmitted, known as Free Space Path
Loss (FSPL). We can use FSPL as our transmission error rate, giving the
following expression: $Error Rate = {(\frac{4 \pi d}{\lambda})}^2$ where $d$ is
the distance between nodes in metres and $\lambda$ is the wavelength of the
electromagnetic wave used in transmission. As much of space communications
utilizes the Ka-band of frequencies (27--40 GHz) we opted to use a transmission
frequency of 30Ghz. The transmission wavelength can be then calculated according
to $\lambda = \frac{c}{f}$, where $c$ is the speed of light and $f$ is the
transmission frequency, giving a transmission wavelength of about 9.99~mm.
Propagation delay is a simple function of distance and the speed of light. The
input of the physics engine is a time $t$ from some preset initial conditions
which outputs the state of all entities.

>>>>

Messages between entities were assumed to be sent at the speed of light in a vacuum, as all
forms of radio, lasers, or other wireless messages are forms of electromagnetic radiation,
and thus travel at the speed of
light. Since the propagation delay in an IPN is much higher than in terrestrial networks, other
delays such as queuing or processing delays were ignored as being negligible.

Based on these simplifications, a physical simulation with several goals. To
calculate if a line of sight could be made between two communicating entities,
that is if a message can be sent, to calculate the error rate when sending a
message, and to calculate the message propagation delay for the message to be
sent. Line of sight was achieved using simple geometry calculations. (See
appendix) All entities are able to block signals if the ray passes through the
radius of the entity. One of the largest factors contributing to transmission
error is the distance travelled by the electromagnetic signal between
transmitting and receiving nodes. By generalizing Friis' transmission formula\cite{Friis}
for isotropic emitters and receivers, we can obtain the ratio of signal
intensity received to signal intensity transmitted, known as Free Space Path
Loss (FSPL). We can use FSPL as our transmission error rate, giving the
following expression: $Error Rate = {(\frac{4 \pi d}{\lambda})}^2$ where $d$ is
the distance between nodes in metres and $\lambda$ is the wavelength of the
electromagnetic wave used in transmission. As much of space communications
utilizes the Ka-band of frequencies (27--40 GHz)\cite{Morabito_Hastrup} we opted to use a transmission
frequency of 30Ghz. The transmission wavelength can be then calculated according
to $\lambda = \frac{c}{f}$, where $c$ is the speed of light and $f$ is the
transmission frequency, giving a transmission wavelength of about 9.99~mm.
Propagation delay is a simple function of distance and the speed of light. The
input of the physics engine is a time $t$ from some preset initial conditions
which outputs the state of all entities.
